Quantum Oracles - How to Transform Classical Problems into Quantum ones

### 2024-08-21 latex/paper.tex
updated paper

For this diagram, it's expected that the player is a rational agent, which always plays aiming to win, and the dealer is a random agent, choosing randomly its decisions.

Nessa estrutura, é previsto que o jogador seja um agente racional, e o dealer uma máquina com ações aleatórias. Assim, o jogador sempre visa o seu próprio benefício, enquanto o dealer age pela sorte.Tal comportamento pode ser visto nas folhas da árvore do qual, sempre que o player é o próximo jogador, sua ação é apenas atirar no adversário, enquanto o dealer ainda possui a possibilidade de entregar o jogo atirando em si próprio, mesmo havendo apenas uma bala na arma e, pela lógica do jogo, ser uma bala verdadeira.\\
Seguindo essa estrutura, podemos simular os possíveis caminhos e verificar a melhor estratégia.

\begin{center}
	\includegraphics[scale=0.6]{optimal_player_strategy.png}
	\captionof{figure}{Buckshot Roulette clássico - melhor estratégia}
	\label{fig:classical-model-bckr-optimal-strategy}
\end{center}

Após testar os caminhos possíveis, o melhor resultado obtido foi esse apresentado acima em \ref{fig:classical-model-bckr-optimal-strategy}. Com um pouco de investigação, foi possível entender que essa estratégia se baseia no jogador começar atirando no dealer. Isso acontece, pois, ao seguir tal caminho, ele tem uma chance a menos de perder a rodada ao atirar em si mesmo logo no começo da partida.

\begin{table}[!h]
	\begin{center}
		\begin{tabular}{ |c|c|c|c| } 
			\hline
			rodada & ação & resultado da ação & resultado da partida \\
			\hline
			1 & player atira no dealer  & real & player ganha\\
			\hline
			1 & player atira no dealer  & fake & -\\
			\hline
			2 & dealer atira no player  & real & dealer ganha\\
			\hline
			2 & dealer atira no player  & fake & -\\
			\hline
			2 & dealer atira nele mesmo  & real & player ganha\\
			\hline
			2 & dealer atira nele mesmo  & fake & -\\
			\hline
			3 & player atira no dealer  & real & player ganha\\
			\hline
			3 & dealer atira no player & real & dealer ganha\\
			\hline
			3 & dealer atira nele mesmo  & real & player ganha\\
			\hline
		\end{tabular}
		\caption{melhor estratégia - possíveis resultados}
	\end{center}
\end{table}

>>>>

For this diagram, it's expected that the player is a rational agent, which always plays aiming to win, and the dealer is a random agent, choosing randomly its decisions. Due that, it's possible to see in the image \ref{fig:classical-model-bckr} that the leafs that was reached by the player, has only one possible value, Shoot, but those reached by the dealer, has two, Shoot himself or his opponent, once he's a random agent.

Using this tree, we can create an algorithm to simulate this game multiple times, and then try to find a possible solution.

After testing multiple possible paths, the best one was given by the path which the player starts shooting the dealer. After Analyzing this very strategy, the conclusion is that, this is the best strategy, because the player has less chances to die, once he doesn't have the chance of killing himself right away at the beginning.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.5]{optimal_player_strategy.png}
	\caption{Classical Buckshot Roulette - Best Strategy}
	\label{fig:classical-model-bckr-optimal-strategy}
\end{figure}

\begin{table}[!h]
	\begin{center}
		\begin{tabular}{ |c|c|c|c| } 
			\hline
			Bullet & Action & action result & shoot result \\
			\hline
			1 & player shoots dealer  & real & player wins\\
			\hline
			1 & player shoots dealer  & fake & -\\
			\hline
			2 & dealer shoots player  & real & dealer wins\\
			\hline
			2 & dealer shoots player  & fake & -\\
			\hline
			2 & dealer shoots himself  & real & player wins\\
			\hline
			2 & dealer shoots himself  & fake & -\\
			\hline
			3 & player shoots dealer  & real & player wins\\
			\hline
			3 & dealer shoots player & real & dealer wins\\
			\hline
			3 & dealer shoots himself & real & player wins\\
			\hline
		\end{tabular}
		\caption{Best Strategy - Analyzing the possible paths}
	\end{center}
\end{table}

%% add the path which the player shoots himself
